Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
tweaks

Domain-specific data interfaces (Section~\ref{object-data-interfaces}) allow
co-design between applications and the storage system. Malacology supports
custom object interfaces in RADOS that require interface implementations to
installed on the storage devices in the system, supports the evolution of
interfaces through automatic system-wide versioning and installation through
the service metdata interface (Section~\ref{service-metadata}). We evaluate
the performance of installing a new version of an interface in the cluster,
which is an important metric for applications that are designed with
frequently evolving interfaces.

@@

Figure~\ref{fig:propdelay} shows the lower bound cost for updates in a large
cluster. In the experiment labeled "120 OSD (RAM)" a cluster of 120 OSDs (10
OSDs x 12 servers) using an in-memory data store were deployed, showing a
latency of less than 54 ms with a probability of 90\% and a worst case latency
of 194 ms. These costs demonstrate the penality of distributing the interface
in a large cluster. In In practice the costs are, in addition to cluster-wide
propagation of interface updates, includes the network round-trip to the
interface management service, the Paxos commit protocol, and other factors
such as system load. By default Paxos proposals occur periodically with a 1
second interval in order to accumulate updates. In a minimum, realistic quorum
of 3 monitors using HDD-based storage, we were able to decrease this interval
to an average of 222 ms.

>>>>

Domain-specific data interfaces (Section~\ref{object-data-interfaces}) allow
co-design between applications and the storage system. Malacology supports
custom object interfaces in RADOS that require interface implementations to
be installed on the storage devices in the system, supporting the evolution of
interfaces through automatic system-wide versioning and installation through
the service metdata interface (Section~\ref{service-metadata}). We evaluate
the performance of installing a new version of an interface in the cluster,
which is an important metric for applications that are designed with
frequently evolving interfaces.

@@

Figure~\ref{fig:propdelay} shows the lower bound cost for updates in a large
cluster. In the experiment labeled "120 OSD (RAM)" a cluster of 120 OSDs (10
OSDs x 12 servers) using an in-memory data store were deployed, showing a
latency of less than 54 ms with a probability of 90\% and a worst case latency
of 194 ms. These costs demonstrate the penality of distributing the interface
in a large cluster. In practice the costs include, in addition to cluster-wide
propagation of interface updates, the network round-trip to the
interface management service, the Paxos commit protocol itself, and other factors
such as system load. By default Paxos proposals occur periodically with a 1
second interval in order to accumulate updates. In a minimum, realistic quorum
of 3 monitors using HDD-based storage, we were able to decrease this interval
to an average of 222 ms.
